Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, $h \in \dcross_H(\bm{t})$, and $v \in \dcross_V(\bm{t})$.

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    All the following statements are true:
    \myenums{
        \item For each $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, we have:

        \myenums{
            \item $\contained_{R_{k-2}}(\bm{t}) \ne \emptyset$.

            \item Denote by $h$ the full segment of $\bm{t}[k-2]$. 
            For any $r \in \contained_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r, h, \bm{t}[k-1])$ belongs to $\J_2$.
        }

>>>>

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have 
        \myitems{
            \item $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$;
            \item $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. 
        }

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    All the following statements are true:
    \myenums{
        \item Consider any $(k-1)$-tuple $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$. Denote by $h$ the full segment of $\bm{t}[k-2]$. Then, for any $r \in \contained_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r, h, \bm{t}[k-1])$ must belong to $\J_2$.
